\documentstyle[12pt]{report}
\parskip 0.20in
\textheight 8.75in
\textwidth 6.0in
\topmargin -0.25in
\oddsidemargin 0.40in

\begin{document}
\baselineskip 0.30in

\setcounter{page}{43}

\section{Bibliography}

H. Abelson and G.J. Sussman, Structure and Interpretation of Computer
Programs, (1985) MIT Press

A.V. Aho, J.E. Hopcroft, and J.D. Ullman, The Design and Analysis of
Computer Algorithms, (1974) Addison Wesley

M.F. Barnsley, Fractals Everywhere, (1988), Academic Press

E.B. Baum, ``What size Net gives valid generalization'', preprint

E.B. Baum, ``Complete Representations for Learning from Examples''

E.B. Baum, ``On the Capabilities of multilayer perceptrons'', Journal
of Complexity.

D.S. Broomhead, R. Jones, and G.P. King, ``Topological Dimension and
local coordinates from time series data'', Journal of Physics A,
20 (1987) 563 - 569

M. Casdagli, ``Nonlinear Prediction of Chaotic Time Series'', Technical
Report, Queen Mary College, London (1988)

T.M. Cover and P.E. Hart, ``Nearest Neighbor Pattern Classification,''
IEEE Transactions on Information Theory, IT-13:1 (1967) 21 - 27.

J.D. Cowan and D.H. Sharp, ``Neural Nets'', Technical Report
LA-UR-87-4098, Los Alamos National Labs (1987)

J.P. Crutchfield, J.D. Farmer, N.H. Packard, and R.S. Shaw, ``Chaos'',
Scientific American, 254(12) (1986) 46 - 57

J.D. Farmer and J.J. Sidorowich, ``Exploiting Chaos to Predict the
Future and Reduce Noise'', Evolution, Learning and Cognition (1988)
World Scientific Press 

J.A. Feldman and D.H. Ballard, ``Connectionist Models and Their
Properties,'' Cognitive Science, 6 (1982) 205 - 254

M.R. Garey and D.S. Johnson, Computers and Intractibility, a Guide to
the Theory of NP-Completeness, (1979), W.H. Freeman and Co.

J.E. Hafstrom, Introduction to Analysis and Abstract Algebra, (1967)
W.B. Saunders Co.

D.O. Hebb, Organization of Behavior, (1949) Jon Wiley and Sons

D. Hillis, The Connection Machine (1986) MIT Press

G.E. Hinton, ``Learning distributed representations of concepts,''
Proceedings of the Eighth Annual Conference of the Cognitive Science
Society, (1986) Erlbaum Associates

G.E. Hinton and J.A. Anderson, Parallel Models of Associative Memory
(1981) Erlbaum Associates

J.J. Hopfield and D.W. Tank, ``Neural Computations of Decisions in
Optimization Problems,'' Biological Cybernetics 52 (1985) 141

T. Kohonen, Self Organization and Associative Memory, (1984) Springer
Verlag 

E. Kreyszig, Advanced Engineering Mathematics, (1979) John Wiley and Sons

A.S. Lapedes and R.M. Farber, ``Nonlinear Signal Processing Using
Neural Networks: Prediction and System Modeling, Technical Report Los
Alamos National Labs (1987)

A.S. Lapedes and R.M. Farber, ``How Neural Nets Work'' Technical
Report Los Alamos National Labs (1988)

L. Leithold, The Calculus with Analytic Geometry, (1976) Harper and Row

M. Mansfield, Introduction to Topology, (1963) Van Nostrand

J.L. McClelland and D.E. Rumelhart, Parallel Distributed Processing:
Explorations in the Microstructure of Cognition, (1986) MIT Press

W.S. McCulloch and W.H. Pitts, ``A logical calculus of ideas immanent
in nervous activity,'' Bulletin of Mathematical Biophysics, 5, (1943)
115 - 133

M.L. Minsky, Computation: Finite and Infinite Machines, (1967)
Prentice Hall, Inc.

M.L. Minsky, The Society of Mind, (1986) Simon and Schuster.

M. Minsky and S. Papert, Perceptrons, (1969) MIT Press.

A. Newell and H.A. Simon, Human Problem Solving (1972) Prentice Hall

S. Omohundro, ``Efficient algorithms with neural network behavior'',
Complex Systems 1 (1987) 273 - 347

W. H. Press, B. P. Flannery, S. A. Teukolsky, and W. T.
Vetterling, Numerical Recipies: The Art of Scientific Computing,
(1986) Cambridge University Press.

F. Richman, Number Theory : An Introduction to Algebra, (1971) Brooks
Cole Publishing Co.

F. Rose, Into the Heart of the Mind, (1984) Vintage

F. Rosenblatt, Principles of Neurodynamics: Perceptrons and the Theory
of Brain Mechanisms, (1961) Spartan Books.

R. Sedgewick, Algorithms, (1983) Addison Wesley

T.J. Sejnowski and C.M. Rosenberg, ``Parallel Networks that learn to
pronounce English text,'' Complex Systems 1:1 (1987) 145 - 168

L. Smith, Linear Algebra, (1978) Springer Verlag

J. Theiler, ``Quantifying Chaos: Practical Estimation of the Correlation
Dimension'', PhD. Thesis Cal. Tech (1987)

L.G. Valiant, ``A Theory of the Learnable,'' Communications of the
ACM, 27:11 (1984) 1134 - 1142

S. Wolfram, Theory and Applications of Cellular Automata, (1986) World
Scientific Publishing Co.

D. Wolpert, ``A Benchmark for how well Neural Nets Generalize'',
Biological Cybernetics, 61, (1989) 303 - 313

D. Wolpert, ``Constructing a generalizer superior to NETtalk via a
mathematical theory of generalization'', Neural Networks, 3, (1990)
445-452

D. Wolpert, ``A mathematical theory of generalization'', Complex
Systems, 4:2 (1990) 151-249

D. Wolpert, ``Improving the performance of generalizers via
time-series-like preprocessing of the learning set'', LA-UR-90-401,
submitted to IEEE PAMI.

\end{document}
